Can We Crunch the Social Graph on the Cheap?

### 2011-01-26 doc/hotpar2011/softxmt-hotpar2011.tex
new abstract

  Large, sparse, irregular graphs map poorly to the memory systems of
  commodity hardware. The scale of emerging real world datasets
  presents a challenge for straightforward algorithms which will run
  inefficiently due to many high-latency accesses.  Pervasive
  parallelism can tolerate that latency, but the only large-scale
  implementation of the technique is the Cray XMT, an expensive,
  non-commodity machine.

  If we can adapt the XMT's programming model to commodity hardware,
  we can dramatically improve performance without resorting to
  expensive custom systems. This paper presents a runtime for latency
  tolerance through the use of parallel lightweight contexts, along
  with our plans for scaling up to multiple nodes. Our analysis shows
  the feasibility of our approach.
\end{abstract}

>>>>

  Crunching large graphs is the basis of many emerging applications,
  such as social network analysis and bioinformatics. Graph analytics
  algorithms exhibit little locality and therefore present significant
  performance challenges. Hardware multithreading systems (e.g, Cray
  XMT) showed that with enough concurrency, we can tolerate long
  latencies. Unfortunately, this solution is not available with
  commodity parts.

  Our goal is to develop a latency-tolerant system built out of
  commodity parts and mostly in software. The proposed system includes
  a runtime that supports a large number of lightweight contexts,
  full-empty synchronization and a memory manager that provides a
  high-latency but high-bandwidth global shared memory. This paper
  lays out the vision for our system, and justifies its feasibility
  with a performance analysis of the runtime for latency tolerance.

% Our analysis shows the feasibility of our
%   approach.

% To that end we developed a new runtime system that supports
%   a large number of lightweight contexts, together with full-empty
%   synchronization primitives and a large global address space.

% To that end, we propose a
%   new runtime system that is able to sustain a large number of active
%   threads

%  XMT-like properties, implemented
%   with commodity components. This paper presents a runtime for latency
%   tolerance, along with our plans for scaling up to multiple
%   nodes. Our analysis shows the feasibility of our approach.

%   Large, sparse, irregular graphs map poorly to the memory systems of
%   commodity hardware. The scale of emerging real world datasets
%   presents a challenge for straightforward algorithms which will run
%   inefficiently due to many high-latency accesses. Pervasive
%   parallelism can tolerate that latency, but the only large-scale
%   implementation of the technique is the Cray XMT, an expensive,
%   non-commodity machine.

%   If we can adapt the XMT's programming model to commodity hardware,
%   we can dramatically improve performance without resorting to
%   expensive custom systems. This paper presents a runtime for latency
%   tolerance through the use of parallel lightweight contexts, along
%   with our plans for scaling up to multiple nodes. Our analysis shows
%   the feasibility of our approach.
\end{abstract}
